Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-24 paper/paper.tex
pass on V.0

The goal of our study is to assess reliability of \js\ engines by
leveraging implementation diversity. We organized our study in three
parts. First, we report on the conformance of the engines we analyzed
using the official Test262 conformance test suite for
EcmaScript~\cite{ecma262-conformance-suite}
(Section~\ref{sec:stability}). In the limit, bugs would have low
relevance if the engines are too unreliable. Second, we report results
obtained with test transplantation
(Section~\ref{sec:transplantation}). The rationale is that the domain
of possible inputs is too large; consequently, we expect that test
suites written for a given engine cover scenarios and corner cases
uncovered by another engine.\Comment{ To sum, we conjecture that test
  cases written for one engine could reveal bugs in different engines
  as opposed to only manifesting false alarms.} Third, we analyzed the
impact of using cross-engine differential testing to find bugs
(Section~\ref{sec:cross-engine-diff-testing-results}). Differential
testing has been used in several contexts to address the oracle
problem~\cite{barr-etal-tse2015}. Intuitively, using differential
testing to find functional bugs across engine implementation could be
promising.

@@

\vspace{1ex}
\noindent\textbf{Summary of Bugs.}~Figures~\ref{fig:stacked-engine}
and~\ref{fig:stacked-technique} show bugs reports per engine and
technique, respectively. Each stacked bar breaks down the bugs per
status. Note that several of these bugs were already fixed and
incorporated in the latest release of the corresponding
engines. Overall, discarding bug report with the ``new'' status, we
reported a total of \noBugsTotalConfirmed{} bugs. Considering the
engines, the majority of bug reports targeted \chakra\ and
\jsc. Considering the techniques, the number of bug reports issued
and confirmed were similar. We found, however, that the cost of
inspecting \Fix{...elaborate...}

%% It is
%% also worth noting that several of these reports hold the status
%% ``new'', which indicates that they were not reviewed yet by the
%% development team. Note also that we did not find bugs in the Mozilla
%% \smonkey\ engine.

\begin{figure}[t!]
  \centering
  \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
    \includegraphics[trim=0 190 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
    \vspace{-5ex}
  }\\
  \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
    \includegraphics[trim=0 180 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
    \vspace{-5ex}        
  }
  \caption{\label{fig:summary}Summary of bug reports.}
\end{figure}

@@

\begin{wraptable}[12]{r}{0.25\textwidth}
  \vspace{-3ex}
  \centering
  \caption{\label{tab:test262}Percentage of passing tests on
    the Test262 conformance suite.}
  \small
  \begin{tabular}{crr}
    \toprule
    engine & \% passing \\
    \midrule
    \jsc{} & 92\%\\
    \veight{} & 95\% \\
    \chakra{} & 75\% \\    
    \smonkey{} & 93\% \\
    \bottomrule
  \end{tabular}
  \normalsize
\end{wraptable}

We used the official conformance test suite
Test262~\cite{ecma262-conformance-suite} to evaluate conformance of
engines to the \js\ current standard. As it is acceptable to release
engines fulfilling the specification only partially~\cite{kangax}, it
is expected that engines do not fully pass this test. However, we
expect that results provide indication of engine's maturity. In the
limit, it is not desirable to flood bug reports on engines at early
stages of development. We ran the suite once a day for seven
consecutive days from the period of 16 to 22 of August,
2018. Table~\ref{tab:test262} shows the average number of passing
tests over this period. The variance of results was negligible; for
that reasons, we omited standard deviations. We noticed that all four
engines we analyzed but \chakra{} use some variant of the Test262
suite as part of their regression process, but we used the same
version in this experiment; the one available from the Test262 web
site~\cite{ecma262-conformance-suite}. Results show that there are
still many unsupported cases as can be observed from the percentages
in the table, but the number of passing tests is high, with
\veight\ and \smonkey\ performing better compared to others and
\chakra\ performing well worse than others. It is important to
highlight that failures in this conformance test suite indicates
missing features as opposed to bugs. However, note that \chakra\ is
both the engine that has the lowest passing ratio in the conformance
test suite and the one we were able to find more bugs. Although it is
possible to find correlation between the percentage of passing tests
in the conformance suite (as per Table~\ref{tab:test262}) and reliability as
measured by the number of bugs found (as per
Figure~\ref{fig:summary}), we do not not imply causality.

>>>>

The goal of our study is to assess reliability of \js\ engines by
leveraging implementation diversity. We organized our study in three
parts. First, we report on the conformance of the engines we studied
using the official Test262 conformance
suite~\cite{ecma262-conformance-suite}
(Section~\ref{sec:stability}). In the limit, bugs would have low
relevance if the engines are too unreliable. Second, we report results
obtained with test transplantation
(Section~\ref{sec:transplantation}). The rationale is that developers
consider different goals when writing test cases--suites written for a
given engine should cover scenarios not covered by a different
engine. Third, we analyzed the impact of using cross-engine
differential testing to find bugs
(Section~\ref{sec:cross-engine-diff-testing-results}). The rationale
is that bugs may be detected using inputs which are similar to those
already tested. Our broad goal is to evaluate ability of these simple
diversity-aware techniques in bug finding.

@@

\vspace{1ex}
\noindent\textbf{Summary of Bugs.}~Figure~\ref{fig:summary} shows the
number of bug reports found per engine (\ref{fig:stacked-engine}) and
technique (\ref{fig:stacked-technique}). Each stacked bar breaks down
the bugs per status (\eg{}, ``1-New''). The prefix number serves to
indicate the ordering that status labels are assigned. Note that
several of these reports have the label ``3-Fixed'', indicating that
bug fixes have been incorporated into the code already.\Comment{
  Depending on the issue date, the fix may be in the latest release of
  the corresponding engines.} Overall, discarding bug report with the
``1-New'' status, we reported a total of \noBugsTotalConfirmed{}
bugs. We found that the majority of bug reports targeted the engines
from Microsoft and Apple. Considering the techniques, the number of
bug reports were similar, if we consider only those confirmed or
fixed. Most of these bugs are of moderate severity. All in all, these
simple techniques seem promising to improve reliability of engines
that continuously evolve with their specifications.

%% We found,
%% however, that the cost of inspecting \Fix{...elaborate...}
%% It is
%% also worth noting that several of these reports hold the status
%% ``new'', which indicates that they were not reviewed yet by the
%% development team. Note also that we did not find bugs in the Mozilla
%% \smonkey\ engine.

\begin{figure}[h!]
  \centering
  \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
    \includegraphics[trim=0 190 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
    \vspace{-5ex}
  }\\
  \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
    \includegraphics[trim=0 180 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
    \vspace{-5ex}        
  }
  \caption{\label{fig:summary}Summary of bug reports.}
\end{figure}

@@

We used the official conformance test suite
Test262~\cite{ecma262-conformance-suite} to evaluate conformance of
engines to the \js\ current standard. As it is acceptable to release
engines fulfilling the specification only partially~\cite{kangax}, it
is expected that engines do not fully pass this test. However, we
expect that results provide indication of engine's maturity. In the
\begin{wraptable}[10]{r}{0.25\textwidth}
%  \vspace{-3ex}
  \centering
  \caption{\label{tab:test262}Percentage of passing tests on
    the Test262 conformance suite.}
  \small
  \begin{tabular}{crr}
    \toprule
    engine & \% passing \\
    \midrule
    \jsc{} & 92\%\\
    \veight{} & 95\% \\
    \chakra{} & 75\% \\    
    \smonkey{} & 93\% \\
    \bottomrule
  \end{tabular}
  \normalsize
  \vspace{-3ex}  
\end{wraptable}
limit, it is not desirable to flood bug reports on engines at early
stages of development. We ran the suite once a day for seven
consecutive days from the period of 16 to 22 of August,
2018. Table~\ref{tab:test262} shows the average number of passing
tests over this period. The variance of results was negligible; for
that reasons, we omited standard deviations. We noticed that all four
engines we analyzed but \chakra{} use some variant of the Test262
suite as part of their regression process, but we used the same
version in this experiment; the one available from the Test262 web
site~\cite{ecma262-conformance-suite}. Results show that there are
still many unsupported cases as can be observed from the percentages
in the table, but the number of passing tests is high, with
\veight\ and \smonkey\ performing better compared to others and
\chakra\ performing well worse than others. It is important to
highlight that failures in this conformance test suite indicates
missing features as opposed to bugs. However, note that \chakra\ is
both the engine that has the lowest passing ratio in the conformance
test suite and the one we were able to find more bugs. Although it is
possible to find correlation between the percentage of passing tests
in the conformance suite (as per Table~\ref{tab:test262}) and reliability as
measured by the number of bugs found (as per
Figure~\ref{fig:summary}), we do not not imply causality.
